Reply To Examiners

### 2014-05-04 answer_thesis_examiner/chap2.tex
auto

@@

The Examiner also suggestion the inclusion of several particular references into \textbf{the literature review}.
I really appreciate the examiner effort in pointing out specific references \cite{Argenti_GRSM_2013, Lee_RSReviews_1994, Cetin_ProcSPIE_2000, White_ProcSPIE_1994, Sattar_TIP_1997, Wang_TIP_2004, Nielsen_2012_ICASSP}.
They, and some other articles, have been included in the thesis.

>>>>

\replyToComment
    {A more comprehensive review of the relevant SAR/POLSAR speckle filters should be included.}
    {The most recent review \cite{Argenti_GRSM_2013} has been included together with several other publications \cite{Lee_RSReviews_1994, Cetin_ProcSPIE_2000, White_ProcSPIE_1994, Sattar_TIP_1997, Wang_TIP_2004, Nielsen_2012_ICASSP}}

\replyToComment
    {Whereever possible, samples of SAR/POLSAR images with these three types of features (i.e. homogeneous, textured and strong scatterer) should be used to evaluate the effectiveness of the proposed models.}
    {In the section to evaluate speckle filters, various different patterns had been studied. Also the MSE evaluation which includes bias and variance evaluation are shown to be able to evaluate the effectiveness of different speckle filters in terms of radiometric preservation and speckle noise reduction respectively.}

%The Examiner also suggestion the inclusion of several particular references into \textbf{the literature review}.
%I really appreciate the examiner effort in pointing out specific references \cite{Argenti_GRSM_2013, Lee_RSReviews_1994, Cetin_ProcSPIE_2000, White_ProcSPIE_1994, Sattar_TIP_1997, Wang_TIP_2004, Nielsen_2012_ICASSP}.
%They, and some other articles, have been included in the thesis.

@@
